\Title

### 2021-01-12 manuscript/manuscript.tex
Put tildes after enumerating subplots on captions

\begin{figure}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-window-size.pdf}
    \caption{
        Gradient-boosted equivalent sources performance against window size.
        Window sizes are given as a fraction of the dimensions of the synthetic
        survey area.
        (a) Root-mean-squared error between predictions and target grid using
        non-boosted sources (orange dashed line) and gradient-boosted
        equivalent sources (blue dots) for different window sizes. Each RMS
        error is the mean of the RMS produced by the same set of parameters but
        with different random seeds.
        (b) Ratio between the computational times needed to fit the
        gradient-boosted and the non-boosted equivalent sources, respectively
        (the fitting time ratio for the non-boosted equivalent sources is
        therefore equal to one).
}
    \label{fig:gradient-boosted-window-size}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
    \caption{
        Gradient-boosted equivalent sources performance against amount of
        overlap.
        (a) Root-mean-squared error between predictions and target grid using
        non-boosted sources (orange dashed line) and gradient-boosted
        equivalent sources (blue dots) for different amount of overlap. Each
        RMS error is the mean of the RMS produced by the same set of parameters
        but with different random seeds.
        (b) Ratio between the computational times needed to fit the
        gradient-boosted and the non-boosted equivalent sources, respectively
        (the fitting time ratio for the non-boosted equivalent sources is
        therefore equal to one).
    }
    \label{fig:gradient-boosted-overlap}
\end{figure}

>>>>

\begin{figure}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-window-size.pdf}
    \caption{
        Gradient-boosted equivalent sources performance against window size.
        Window sizes are given as a fraction of the dimensions of the synthetic
        survey area.
        (a)~Root-mean-squared error between predictions and target grid using
        non-boosted sources (orange dashed line) and gradient-boosted
        equivalent sources (blue dots) for different window sizes. Each RMS
        error is the mean of the RMS produced by the same set of parameters but
        with different random seeds.
        (b)~Ratio between the computational times needed to fit the
        gradient-boosted and the non-boosted equivalent sources, respectively
        (the fitting time ratio for the non-boosted equivalent sources is
        therefore equal to one).
}
    \label{fig:gradient-boosted-window-size}
\end{figure}

@@

\begin{figure}
    \includegraphics[width=\linewidth]{figs/gradient-boosted-overlap.pdf}
    \caption{
        Gradient-boosted equivalent sources performance against amount of
        overlap.
        (a)~Root-mean-squared error between predictions and target grid using
        non-boosted sources (orange dashed line) and gradient-boosted
        equivalent sources (blue dots) for different amount of overlap. Each
        RMS error is the mean of the RMS produced by the same set of parameters
        but with different random seeds.
        (b)~Ratio between the computational times needed to fit the
        gradient-boosted and the non-boosted equivalent sources, respectively
        (the fitting time ratio for the non-boosted equivalent sources is
        therefore equal to one).
    }
    \label{fig:gradient-boosted-overlap}
\end{figure}
